Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
something about kum
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51100 72bbbca6-d526-0410-a7d9-f06f51895060

The low recall for Kazakh can be explained by the fact that the corpus is much bigger, giving 
more hapax words and proper names. There were 403 out-of-vocabulary words out of 1,000 in the Kazakh list.
Of these 403, 160 were proper nouns, and 148 were common nouns. The lower precision for the 
Tatar transducer can be partly explained by the less transparent orthography of Tatar.

>>>>

The low recall for Kazakh can be explained by the fact that the corpus is much bigger, giving 
more hapax words and proper names. There were 403 out-of-vocabulary words out of 1,000 in the Kazakh list.
Of these 403, 160 were proper nouns, and 148 were common nouns. The lower precision for the 
Tatar transducer can be partly explained by the less transparent orthography of Tatar.  Due to limited access to native Kumyk speakers, the authors performed precision themselves based on their admittedly incomplete knowledge of the language.  Recall is low for Kumyk due mostly to some systematic gaps in the morphotactics, such as lack of attributive analyses in several continuation lexica.
